Do larger catchments respond different to forest cover change? Re-analysing a global data set.

### 2021-09-27 paper/Forest_and_Water/Forest_and_Water.Rmd
changes WV 27092021

As a result the objective of this paper is to 1) enhance the data set from @zhang2017 with further watersheds (such as from @filoso2017) and spatial coordinates and 2) to analyse the possibility of non-linear, interactions and partial effects of the different factors and variables in the data using generalised linear (GLM) and generalised additive models (GAM @wood2006). Finally, this work aims to point to further research that can expand this area of work, based on the collected data, to better understand the impact of forest cover change on streamflow.

@@

- the type of analysis, i.e. paired catchment studies, modelling, time series analysis etc.

- the age of the study, assuming that historical studies might not have had the ability to measure at the accuracy that currently is available to researchers, or that more careful historical attention to detail in field studies might have been lost more recently due to reductions in research investment.

@@

<!-- analysis -->
```{r model2, echo = F}
require(mgcv)
linear_model_all_log <- gam(log10(DeltaQf_perc/100+1) ~ DeltaF_perc + Area_km2 + Pa_mm, data = Zhang_all)
summary(linear_model_all_log)
gam.check(linear_model_all_log)
```

>>>>

As a result the objective of this paper is to 1) enhance the data set from @zhang2017 with further watersheds (such as from @filoso2017) and spatial coordinates and 2) to analyse the possibility of non-linear, interactions and partial effects of the different factors and variables in the data using generalised linear (GLM) and generalised additive models (GAM @wood2006).

* the type of analysis, i.e. paired catchment studies, modelling, time series analysis etc.

* the age of the study, assuming that historical studies might not have had the ability to measure at the accuracy that currently is available to researchers, or that more careful historical attention to detail in field studies might have been lost more recently due to reductions in research investment.

Finally, this work aims to point to further research that can expand this area of work, based on the collected data, to better understand the impact of forest cover change on streamflow.

@@

@@

<!-- analysis -->
```{r model2, echo = F}
require(mgcv)
linear_model_all_log <- gam(log10(DeltaQf_perc/100+1) ~ DeltaF_perc + Area_km2 + Pa_mm, data = Zhang_all)
summary(linear_model_all_log)
gam.check(linear_model_all_log)
```
<!-- This shows that Area is not significant -->

<!-- include Lat and Long (later E0) -->

```{r model2a, echo = F}
linear_model_all_log <- gam(log10(DeltaQf_perc/100+1) ~ DeltaF_perc + Area_km2 + Pa_mm + Latitude + Longitude, data = Zhang_all)
summary(linear_model_all_log)
gam.check(linear_model_all_log)
```

<!-- include all the other numerical variables -->

```{r model2a, echo = F}
Zhang_all <- Zhang_all %>%
  mutate(length = To - From)
linear_model_all_log <- gam(log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + log10(Area_km2) + Pa_mm +  Latitude + Longitude + From + length, data = Zhang_all)
summary(linear_model_all_log)
gam.check(linear_model_all_log)
```

<!-- model 2b also include categorical variables -->
```{r model2b, echo = F}

linear_model_all_log <- gam(log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + s(Area_km2, k=3) + s(Pa_mm, k=3) + s(From,k = 3) + s(length, k=3) + Precip_data_type + Assessment_technique + Forest_type + Hydrological_regime, data = Zhang_all)
summary(linear_model_all_log)
gam.check(linear_model_all_log)
```
<!-- model 2c include smooth variables -->

```{r model2c, echo = F}

linear_model_all_log <- gam(log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + s(Area_km2, k=3) + s(Pa_mm, k=3) + s(From,k = 3) + s(length, k=3) + Precip_data_type + Assessment_technique + Forest_type + Hydrological_regime, data = Zhang_all)
summary(linear_model_all_log)
gam.check(linear_model_all_log)
```

No evidence of effect of area

<!-- Should area be log transformed? model 2d -->

```{r model2d, echo = F}

linear_model_all_log <- gam(log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + log10(Area_km2) + s(Pa_mm, k=3) + From + length + Precip_data_type + Assessment_technique + Forest_type + Hydrological_regime + Latitude + Longitude, data = Zhang_all)
summary(linear_model_all_log)
gam.check(linear_model_all_log)
```
```{r}
Zhang_all %>%
  ggplot(aes(Assessment_technique,log10(Area_km2))) + geom_boxplot()
```

```{r}
Zhang_all %>%
  ggplot(aes(DeltaF_perc, log10(DeltaQf_perc/100 + 1), colour = Assessment_technique,size = log10(Area_km2))) + geom_point()
```
```{r}
tiff("flow_forest_byArea.tiff", width = 2000, height = 1400, res = 300)
Zhang_all %>%
  ggplot(aes(DeltaF_perc/100, (DeltaQf_perc/100 + 1), colour = Assessment_technique, size = log10(Area_km2))) + geom_point() +
  theme_bw() + ylab("log10 (fractional change in flow + 1)") +
  xlab("fractional change in forestry") + scale_y_log10() + scale_size_continuous(name = "log10 Area in km2") +
  scale_colour_discrete(name = "Assessment Technique")
dev.off()
```

```{r}
Zhang_all %>%
  ggplot(aes(Latitude, log10(DeltaQf_perc/100 + 1), colour = DeltaF_perc,size = log10(Area_km2))) + geom_point()
```

Check the size distribition of the catchments

```{r}
Zhang_all %>%
  ggplot(aes(Area_km2)) + geom_histogram(fill="blue", bins =50) +
  scale_x_log10()
total <- nrow(Zhang_all)
length(Zhang_all$Area_km2[Zhang_all$Area_km2<10])/total
```
